### 2021-07-10 src/paper/data/share_known_cases.tex
Improve the model fit text and add paragraphs on R_t and vaccinations.

\subsection{Share of Detected Cases}
\label{subsec:appendix_share_known_cases}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation. We use the overall share of known
  cases that was estimated through the case fatality ratio by the
  \href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} for all of 2020 and
  then assume it to be constant as vaccinations of the elderly strongly affect the case
  fatality rate which the project does not account for. To get from an overall share of
  detected cases to the share of cases that is detected in each age group we use that
  asymptomatic cases are much less likely to be detected. As our model covers age
  specific asymptomatic rates this endogenously leads to group specific share known cases
  that verify that infections in younger age groups are under-detected. Starting in 2021
  in addition to the overall numbers of detected cases through symptoms and the share
  known cases, cases are also detected through confirmation of positive rapid tests. This
  leads to an increase in the share of known cases for all age groups but in particular
  for the younger age groups that are covered extensively with rapid tests through the
  rapid test requirement for participating in school.}
\end{figure}

It's noteworthy that the share of detected cases increases rapidly in May for the five to
fourteen year olds. This is a direct result of the mandatory tests in school.

>>>>

\subsection{Share of Detected Cases}
\label{subsec:data_share_known_cases}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/data/testing/assumed_overall_share_known_cases}
  \caption{Share of Detected Cases}
  \label{fig:share_known_cases_data}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation. We use the overall share of known
  cases that was estimated through the case fatality ratio by the
  \href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} for all of 2020 and
  then assume it to be constant as vaccinations of the elderly strongly affect the case
  fatality rate which the project does not account for. Starting in 2021 in addition to
  the overall numbers of detected cases through symptoms and the share known cases, cases
  are also detected through confirmation of positive rapid tests which happens
  endogenously inside the model. For the public holidays of Christmas and Easter we lower
  the share of detected cases as fewer PCR tests are available during public holidays.}
\end{figure}

### 2021-07-10 src/paper/results/fit.tex
Improve the model fit text and add paragraphs on R_t and vaccinations.

%%% WRITE MORE POSITIVELY

This section compares simulated data from our model with empirical data from Germany. We
look at observed infections, the spread of the B.1.1.7 mutation,
vaccinations\comment[id=K]{We fit vaccinations in the population by construction. Maybe
this should go to a different section?} and rapid test demand. Where available we do not
only look at aggregated statistics but also analyze the model fit for age groups and
federal states.

% summary of the fit
Overall, our model achieves an excellent fit of the two waves of infections with few free
parameters (Figure~\ref{fig:aggregated_fit2}. As a result the effective replication
number is similar to that reported by the RKI (see Figure~\ref{fig:fit_r_effective}).
This excellent fit is also achieved for most age groups in Germany. The fit is also good
for many German federal states. Despite, the fact that the number of performed rapid
tests and their distribution in the population results endogenously inside our model we
fit the share of the population with at least a weekly rapid test very well and err on
the side of too few individuals that have ever done a rapid test.

% observed infections
Our fit of the infection rates in Germany between October 2020 and June 2021 is very
good. The incidence in our model follows the shape of the reported incidence almost
perfectly. % The increase in December is somewhat less steep than it was. This can be
% attributed to the large number of cases in nursing homes during that time that our
% model cannot capture because it does not include nursing homes. \comment[id=K]{Write
% about uncertainty and that we take enough simulations to have a stable mean}

\begin{figure}[ht]   % observed infections with single runs
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case_with_single_runs}
  \caption{Fit Over the Full Simulation Time Frame with Single Simulation Runs}
  \floatfoot{\noindent \textit{Note:} The figure shows the weekly incidence rates per
  100,000 people for the reported simulated infections rates. The mean infection rate is
  the thick blue line. Single simulation runs are plotted in lighter and thinner lines.
  The official case numbers as reported by the Robert-Koch-Institut are plotted in black.
  The fit is overall very good. The higher the mean incidence and the stronger the growth
  the more variance there is between simulation runs. We averaged over 30 simulation
  runs.}
  \label{fig:aggregated_fit2}
\end{figure}

% observed infections by age group
Zooming into the different age groups in Figure~\ref{fig:age_group_fit}, we can see that
our model is also able to reproduce the infection rates on this level. Differences
between the age groups allow us to identify the infection probabilities because different
age groups have contacts of different types (e.g. Mostly children go to school, the share
of workers is highest in the 35 to 59 age bracket etc.). There are only three
\textcolor{red}{\ldots}. Firstly, the age group of 80 to 100 year olds due to the absence
of nursing homes in our synthetic population. Secondly, the increase in adolescents in
April. It is surprising that we do not match this increase despite explicitly modeling
the introduction of rapid tests for students. However, it can be expected that every
rapid test in a school setting is followed up by a PCR test while only 82\% of our
population \citep{Betsch2021} demand a confirming PCR test when receiving a positive
rapid test. The last age group where our fit does not fit the empirical curve very well
is the group of 15 to 34 year olds. This group has been touted to have a very active
social life and it has often been suspected that this age group also stayed more socially
active during the pandemic. Since our model does not include either effect it's
unsurprising that the actual case numbers in this group are consistently higher than our
simulated case numbers.\comment[id=K]{Does anyone have an idea why we do not match the
shape from Oct to Dec?}

@@

% observed infections by federal state
Looking at another disaggr
Our states are uniform with respect to their age distribution.

@@

Our fit of the effective replication number $R_t$ closely follows the values reported by
the RKI. \textcolor{red}{ldots}

@@

% fatality rates: MISSING

@@

@@

>>>>

This section compares simulated data from our model with empirical data from Germany. We
look at observed infections (overall as well as by age group and federal state), the
spread of the B.1.1.7 mutation, vaccinations\comment[id=K]{We fit vaccinations in the
population by construction. Maybe this should go to a different section?} and rapid test
demand.

% summary of the fit
Overall, our model achieves an excellent fit of the two waves of infections with few free
parameters (Figure~\ref{fig:aggregated_fit2}. As a result the effective replication
number is similar to that reported by the RKI (see Figure~\ref{fig:fit_r_effective}).
This excellent fit is also achieved for most age groups in Germany. The fit is also good
for many German federal states. Despite, the fact that the number of performed rapid
tests and their distribution in the population result endogenously inside our model we
fit the share of the population with at least a weekly rapid test very well and err on
the side of too few individuals that have ever done a rapid test.

% observed infections
Our fit of the infection rates in Germany between October 2020 and June 2021 is
excellent. The incidence in our model matches both the levels and the shape of the
reported incidence almost perfectly. When the prevalence of the virus is high and during
phases of exponential growth, the effect of random events on the incidence is large. That
is why it's important that we rely on 30 simulation runs with different seed sequences to
average over these random differences and have a stable mean.

\begin{figure}[ht]   % observed infections with single runs
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case_with_single_runs}
  \caption{Fit Over the Full Simulation Time Frame with Single Simulation Runs}
  \floatfoot{\noindent \textit{Note:} The figure shows the daily incidence rate per
  million for the reported simulated infections rates. The mean infection rate is the
  thick blue line. Single simulation runs are plotted in lighter and thinner lines. The
  official case numbers as reported by the RKI are plotted in black. The fit is overall
  very good. The higher the mean incidence and the stronger the growth the more variance
  there is between simulation runs. We averaged over 30 simulation runs.}
  \label{fig:aggregated_fit2}
\end{figure}

% observed infections by age group
Zooming into the different age groups in Figure~\ref{fig:age_group_fit}, we can see that
our model is also able to reproduce the infection rates on this level. Differences
between the age groups allow us to identify the infection probabilities because different
age groups have contacts of different types (e.g. Mostly children go to school, the share
of workers is highest in the 35 to 59 age bracket etc.). There are very few points where
our simulated incidences and the empirical incidences do not
coincide:\comment[id=K]{@Janos: I think you can probably present this better...} Firstly,
the age group of 80 to 100 year olds due to the absence of nursing homes in our synthetic
population. Secondly, the increase in adolescents in April. We model the introduction of
rapid tests for students and do see an increase both in the observed infections and the
share of detected cases among students (see
Figure~\ref{fig:share_known_cases_by_age_group}). However, we follow \cite{Betsch2021}
that 82\% of all rapid tests are followed up with a PCR test. It is likely that that
share is higher for rapid tests that were done in schools. The last age group where our
fit does not fit the empirical curve very well is the group of 15 to 34 year olds. This
group has been touted to have a very active social life and it has often been suspected
that this age group also stayed more socially active during the pandemic. However, our
model does not include either effect because of very little data on both and hence it's
unsurprising that the actual case numbers in this group are consistently higher than our
simulated case numbers.\comment[id=K]{Does anyone have an idea why we do not match the
shape from Oct to Dec?}

@@

% observed infections by federal state
Our model fit is also very good for the different German federal states. This holds not
only for the large states such as North Rhine-Westphalia or Bavaria but also for many
smaller states such as Hessen or Rhineland-Palatinate. This shows that the inclusion of
school vacations and relying on work reductions by \cite{Google2021} combined with the
assortativity of contacts on the county level is sufficient to represent many local
differences.  %
However, admittedly, there are several patterns that our model does not reproduce - for
example because we do not have cross-border travel nor population density. This explains
why our model produces too many infections for federal states such as Schleswig-Holstein
and why it predicts too few infections for states, such as Saxony, bordering high
incidence countries.\comment[id=K]{The Czech Republic had very high numbers in October
(max > 800) but they fell during Nov to 220 and then climbed again to 800 by Jan 12th so
that might be only part of the answer why Saxony had such high numbers.}
However, these missing features are irrelevant for our main conclusions.

@@

Our fit of the effective replication number $R_t$ closely follows the values reported by
the RKI even though we calculate $R_t$ on all infected individuals not just the detected
cases. This explains why the $R_t$ in our simulations is higher during phases where the
share of detected cases falls such as in the fall of 2020 (see
Figure~\ref{fig:share_known_cases_data}) where the RKI underestimated the effective
replication number due to observing a lower share of cases and is lower than the $R_t$
reported by the RKI in spring where the share of known cases increased due to increased
rapid testing.

@@

% B.1.1.7
We fit the proliferation of the B.1.1.7 variant quite exactly despite only introducing a
few cases in January as can be seen in Figure~\ref{fig:fit_share_b117}. Since we only
model B.1.1.7 and do not include other variants B.1.1.7 reaches a share of nearly 100\%
by May while the true rate plateaued at 90\% and B.1.1.7 was then replaced by B.1.617.2
as the dominant variant in June. However, B.1.1.7 still made up over 90\% of all cases in
Germany at the end of our simulation period.

@@

% vaccinations

The fit of the share of vaccinated individuals can be seen in
Figure~\ref{fig:fit_vaccinations}. In Germany, vaccines were rolled according to four
priority groups. The first vaccines were mostly reserved for nursing homes and some
selected professions such as first responders. Since we do not have nursing home
inhabitants in our model, we subtract the first percent of vaccinations which is
equivalent to the share of Germans living in nursing homes. Afterwards, the share of
vaccinated individuals in the population follows the German increase quite exactly. We
took great care to model the prioritization of older individuals and professions that
cannot reduce physical contact easily such as teachers or medical staff (see
Section~\ref{subsec:synthetic_population}. How the share of vaccinated individuals
develops by age group can be seen in Figure~\ref{fig:vaccinations_by_age_group}.

@@

% rapid test demand
